Dummy Coding Categorical Data
========================================================
Stat 2*** 
---------------------------------------------------------
Using the Turkeys data set
### 

```{r}
turk <- read.csv(file="C:\\Users\\Aaron\\Documents\\Datasets\\Turkeys.csv",header=T)
head(turk)
attach(turk)
```
*read.csv(file.choose(),header=T)* can be used to select the file manually.
### 
* There are **3** levels within Origin,   
therefore we must set **1** as a reference and the other **2** as dummy coded variables.  
* The variable we select as the reference is arbitrary.

To do this we will use the **ifelse** statement 
### 
```{r}
Z1 <- ifelse(Origin=="V",1,0)    ## Notice that TWO equals signs must be used
Z2 <- ifelse(Origin=="W",1,0)    
```
* The first number is what the level of Origin will be equal to *if* it's *true*, **1**.  
* The second number is our *Otherwise* statement, **0** .


Creating the interactions of Age with the dummy coded variables 
#### 
```{r}
Z1X <- Z1*Age
Z2X <- Z2*Age
```

A new data frame can now be made which includes the dummy coded variables.
### 

```{r}
turk2 <- data.frame(turk, Z1, Z2, Z1X, Z2X)
turk2
```


